paper1_results_figs_slimmed_50_rr

### 2017-01-03 inst/documents/paper1/old/pap1_figs_slimmed_50_unequal.Rmd
tidy pap1 files into own folder

  #in_cols <- c("exposure","effectiveness_insecticide1","dominance_allele1")  
  #4unequal
  in_cols <- c("exposure","dominance_allele1","selection_coef_allele1","effectiveness_insecticide1")

@@

             #YlGnBu looks really good except that the yellow points are very faint
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold", direction='horizontal')) + 
             theme_bw() +
             theme(legend.position = "bottom") +
             #theme_minimal() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='black', shape=3) +
             #failing to add legend for curtis point
             #scale_fill_manual(name = "Curtis Fig.2", values = 'red', labels = 'test') +
             #scale_size_manual(name = "Curtis Fig.2", values="test") +
             #scale_shape_manual(name = "Curtis Fig.2", values="test") +             
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #4unequal copmment out below
             #NOW can I add a lm fitted to the 0 points abs_diff
             # geom_smooth(data=ggSubset[which(ggSubset$abs_diff==0),], method = "lm", se = FALSE, colour='red', lwd=0.5) +
             # #can I subtley highlight the zero points which are repeated in each plot ?
             # geom_point(data=ggSubset[which(ggSubset$abs_diff==0),], size=0.8, colour='red', shape=2, fill='white') +

             #add text for Curtis point
             geom_label(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"', hjust='"right"'), nudge_x=-0.02, size=3, colour='black')
           )

  # doing the lm outside of ggplot    
  # x1=df_same$exposure 
  # y1=df_same$effectiveness_insecticide1 + df_same$effectiveness_insecticide2
  # 
  # l_mod <- lm(y1 ~ x1)
  # l_mod$coefficients

@@

             theme_bw() +
             theme(legend.position = "bottom") +
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold", direction='horizontal')) + 
             #add point for Curtis inputs
             #geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5)
             #add a lm fitted to where exactly 20% diff
             #geom_smooth(data=df_20pc, method = "lm", se = FALSE,colour='red', lwd=0.5)+
             #can I subtley highlight the zero points which are repeated in each plot ?
             #geom_point(data=df_20pc, size=0.8, colour='red', shape=2) #, fill='white') 
           )

  # doing the lm outside of ggplot    
  # x1=df_20pc$exposure 
  # y1=df_20pc$effectiveness_insecticide1 + df_20pc$effectiveness_insecticide2
  # 
  # l_mod <- lm(y1 ~ x1)
  # l_mod$coefficients
# (Intercept)          x1 
#   1.3914547   0.2904911

>>>>

  #in_cols <- c("exposure","effectiveness_ins1","dominance_allele1")  
  #4unequal
  in_cols <- c("exposure","dominance_allele1","selection_coef_allele1","effectiveness_ins1")

@@

             #YlGnBu looks really good except that the yellow points are very faint
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold", direction='horizontal')) + 
             theme_bw() +
             theme(legend.position = "bottom") +
             #theme_minimal() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2), colour='black', shape=3) +
             #failing to add legend for curtis point
             #scale_fill_manual(name = "Curtis Fig.2", values = 'red', labels = 'test') +
             #scale_size_manual(name = "Curtis Fig.2", values="test") +
             #scale_shape_manual(name = "Curtis Fig.2", values="test") +             
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #4unequal copmment out below
             #NOW can I add a lm fitted to the 0 points abs_diff
             # geom_smooth(data=ggSubset[which(ggSubset$abs_diff==0),], method = "lm", se = FALSE, colour='red', lwd=0.5) +
             # #can I subtley highlight the zero points which are repeated in each plot ?
             # geom_point(data=ggSubset[which(ggSubset$abs_diff==0),], size=0.8, colour='red', shape=2, fill='white') +

             #add text for Curtis point
             geom_label(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_ins1 + effectiveness_ins2', label='"Curtis Fig.2"', hjust='"right"'), nudge_x=-0.02, size=3, colour='black')
           )

  # doing the lm outside of ggplot    
  # x1=df_same$exposure 
  # y1=df_same$effectiveness_ins1 + df_same$effectiveness_ins2
  # 
  # l_mod <- lm(y1 ~ x1)
  # l_mod$coefficients

@@

             theme_bw() +
             theme(legend.position = "bottom") +
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold", direction='horizontal')) + 
             #add point for Curtis inputs
             #geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5)
             #add a lm fitted to where exactly 20% diff
             #geom_smooth(data=df_20pc, method = "lm", se = FALSE,colour='red', lwd=0.5)+
             #can I subtley highlight the zero points which are repeated in each plot ?
             #geom_point(data=df_20pc, size=0.8, colour='red', shape=2) #, fill='white') 
           )

  # doing the lm outside of ggplot    
  # x1=df_20pc$exposure 
  # y1=df_20pc$effectiveness_ins1 + df_20pc$effectiveness_ins2
  # 
  # l_mod <- lm(y1 ~ x1)
  # l_mod$coefficients
# (Intercept)          x1 
#   1.3914547   0.2904911

### 2017-01-03 inst/documents/paper1/old/paper1_results_figs.Rmd
tidy pap1 files into own folder

    #failed hex plot just gave me counts
    # print( ggplot(ggSubset, aes_string(x='exposure', y='effectiveness_insecticide1', colour='mixA_better_seq0.25'))+
    #          geom_hex()
    #        )

    #interesting plot showing where sequence is better is restricted to higher values of exposure and effectiveness 
    print( ggplot(ggSubset, aes_string(x='exposure', y='effectiveness_insecticide1', colour='mixA_better_seq0.25'))+
             #geom_hex()
             geom_point(alpha=0.2)  
           )

    #can I multiply the two effectivenesses together ?
    #aha! yes that's even better
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 * effectiveness_insecticide2, colour=mixA_better_seq0.25))+
             #geom_hex()
             geom_point(alpha=0.2)  
           )

    #i think adding the effectivenesses may give an even better plot
    #and makes it easier for the reader to interpret
    #aha! yes that's even better
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=mixA_better_seq0.25))+

@@

    #facetted 0/1, labelled mix better, seq better
    #if I get this sorted I could try to have +ve & -ve on the same scale
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=seq_better_mixA0.25))+
             facet_grid( ~ seq_better_mixA0.25, labeller=as_labeller( c('0'='adaptive mix better','1'='sequential better'))) +

@@

    #what if I do the difference rather than just 0/1
    #aha! this is close to being the killer plot, just need to get the colour scale right 
    #but the previous one may be clearer
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 * effectiveness_insecticide2, colour=mixA_minus_seq0.25))+
             #geom_hex()
             geom_point(alpha=1) +
             #no adding grey outlines obscures the pattern
             #geom_point(shape=21, colour='grey') +
             #this one does look good but slight potential to see negatives above even though they aren't there
             #could I modify the shapes to be different
             #would a repeated, faceted plot solve that ?
             #scale looks good but colours could do with being denser
             #and I'm not sure that making the points that are close to zero white is a good idea ?
             #although it does mean points that are only a few generations different do not obscure the pattern
             #maybe I could explicitly do Ians 20% thing & colour those white
             scale_colour_gradient2()

@@

    #COOLIO !! I really like this figure.
    library(viridis)
    #facet showing generation differences, labelled mix better, seq better
    #+ve & -ve on the same colour scale
    #failed attempt at getting Curtis point in legend
    #print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mixA_minus_seq0.25, size="Curtis"))+
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mixA_minus_seq0.25))+

@@

    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mixA_minus_seq0.25))+

@@

             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #!!!NOW can I add a lm fitted to the 0 points mixA_minus_seq0.25
             geom_smooth(data=ggSubset[which(ggSubset$mixA_minus_seq0.25==0),], method = "lm", se = FALSE) +
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=ggSubset[which(ggSubset$mixA_minus_seq0.25==0),], size=0.8, colour='lightgrey', shape=2, fill='white') +            
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

  # doing the lm outside of ggplot    
  df_same = ggSubset[which(ggSubset$mixA_minus_seq0.25==0),]
  x1=df_same$exposure 
  y1=df_same$effectiveness_insecticide1 + df_same$effectiveness_insecticide2

@@

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2))+ #, colour=abs_mixA_minus_seq0.25))+

@@

    #i think adding the effectivenesses may give an even better plot
    #and makes it easier for the reader to interpret
    #aha! yes that's even better
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=mix2_better_seq0.25))+

@@

    #facetted 0/1, labelled mix better, seq better
    #if I get this sorted I could try to have +ve & -ve on the same scale
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=seq_better_mix20.25))+
             facet_grid( ~ seq_better_mix20.25, labeller=as_labeller( c('0'='mix better','1'='sequential better'))) +

@@

    #killer plot mix2 vs seq
    library(viridis)
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mix2_minus_seq0.25))+

@@

             #YlGnBu looks really good except that the yellow points are very faint
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #theme_minimal() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             #failing to add legend for curtis point
             #scale_fill_manual(name = "Curtis Fig.2", values = 'red', labels = 'test') +
             #scale_size_manual(name = "Curtis Fig.2", values="test") +
             #scale_shape_manual(name = "Curtis Fig.2", values="test") +             
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

    #modify killer plot mix2 vs seq to add in male exposure prop on x axis
    library(viridis)
    print( ggplot(ggSubset, aes(x=exposure+exposure*male_exposure_prop, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mix2_minus_seq0.25))+

             facet_grid( ~ seq_better_mix20.25, labeller=as_labeller( c('0'='mix better','1'='sequential better'))) +
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure+exposure*male_exposure_prop, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides for both sexes') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2))+ #, colour=abs_mixA_minus_seq0.25))+

>>>>

    #failed hex plot just gave me counts
    # print( ggplot(ggSubset, aes_string(x='exposure', y='effectiveness_ins1', colour='mixA_better_seq0.25'))+
    #          geom_hex()
    #        )

    #interesting plot showing where sequence is better is restricted to higher values of exposure and effectiveness 
    print( ggplot(ggSubset, aes_string(x='exposure', y='effectiveness_ins1', colour='mixA_better_seq0.25'))+
             #geom_hex()
             geom_point(alpha=0.2)  
           )

    #can I multiply the two effectivenesses together ?
    #aha! yes that's even better
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 * effectiveness_ins2, colour=mixA_better_seq0.25))+
             #geom_hex()
             geom_point(alpha=0.2)  
           )

    #i think adding the effectivenesses may give an even better plot
    #and makes it easier for the reader to interpret
    #aha! yes that's even better
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2, colour=mixA_better_seq0.25))+

@@

    #facetted 0/1, labelled mix better, seq better
    #if I get this sorted I could try to have +ve & -ve on the same scale
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2, colour=seq_better_mixA0.25))+
             facet_grid( ~ seq_better_mixA0.25, labeller=as_labeller( c('0'='adaptive mix better','1'='sequential better'))) +

@@

    #what if I do the difference rather than just 0/1
    #aha! this is close to being the killer plot, just need to get the colour scale right 
    #but the previous one may be clearer
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 * effectiveness_ins2, colour=mixA_minus_seq0.25))+
             #geom_hex()
             geom_point(alpha=1) +
             #no adding grey outlines obscures the pattern
             #geom_point(shape=21, colour='grey') +
             #this one does look good but slight potential to see negatives above even though they aren't there
             #could I modify the shapes to be different
             #would a repeated, faceted plot solve that ?
             #scale looks good but colours could do with being denser
             #and I'm not sure that making the points that are close to zero white is a good idea ?
             #although it does mean points that are only a few generations different do not obscure the pattern
             #maybe I could explicitly do Ians 20% thing & colour those white
             scale_colour_gradient2()

@@

    #COOLIO !! I really like this figure.
    library(viridis)
    #facet showing generation differences, labelled mix better, seq better
    #+ve & -ve on the same colour scale
    #failed attempt at getting Curtis point in legend
    #print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2, colour=abs_mixA_minus_seq0.25, size="Curtis"))+
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2, colour=abs_mixA_minus_seq0.25))+

@@

    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2, colour=abs_mixA_minus_seq0.25))+

@@

             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #!!!NOW can I add a lm fitted to the 0 points mixA_minus_seq0.25
             geom_smooth(data=ggSubset[which(ggSubset$mixA_minus_seq0.25==0),], method = "lm", se = FALSE) +
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=ggSubset[which(ggSubset$mixA_minus_seq0.25==0),], size=0.8, colour='lightgrey', shape=2, fill='white') +            
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_ins1 + effectiveness_ins2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

  # doing the lm outside of ggplot    
  df_same = ggSubset[which(ggSubset$mixA_minus_seq0.25==0),]
  x1=df_same$exposure 
  y1=df_same$effectiveness_ins1 + df_same$effectiveness_ins2

@@

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2))+ #, colour=abs_mixA_minus_seq0.25))+

@@

    #i think adding the effectivenesses may give an even better plot
    #and makes it easier for the reader to interpret
    #aha! yes that's even better
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2, colour=mix2_better_seq0.25))+

@@

    #facetted 0/1, labelled mix better, seq better
    #if I get this sorted I could try to have +ve & -ve on the same scale
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2, colour=seq_better_mix20.25))+
             facet_grid( ~ seq_better_mix20.25, labeller=as_labeller( c('0'='mix better','1'='sequential better'))) +

@@

    #killer plot mix2 vs seq
    library(viridis)
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2, colour=abs_mix2_minus_seq0.25))+

@@

             #YlGnBu looks really good except that the yellow points are very faint
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #theme_minimal() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2), colour='red', shape=3) +
             #failing to add legend for curtis point
             #scale_fill_manual(name = "Curtis Fig.2", values = 'red', labels = 'test') +
             #scale_size_manual(name = "Curtis Fig.2", values="test") +
             #scale_shape_manual(name = "Curtis Fig.2", values="test") +             
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_ins1 + effectiveness_ins2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

    #modify killer plot mix2 vs seq to add in male exposure prop on x axis
    library(viridis)
    print( ggplot(ggSubset, aes(x=exposure+exposure*male_exposure_prop, y=effectiveness_ins1 + effectiveness_ins2, colour=abs_mix2_minus_seq0.25))+

             facet_grid( ~ seq_better_mix20.25, labeller=as_labeller( c('0'='mix better','1'='sequential better'))) +
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure+exposure*male_exposure_prop, y=effectiveness_ins1 + effectiveness_ins2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides for both sexes') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_ins1 + effectiveness_ins2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2))+ #, colour=abs_mixA_minus_seq0.25))+

### 2017-01-03 inst/documents/paper1/old/paper1_results_figs_slimmed.Rmd
tidy pap1 files into own folder

  #remove insecticide1 & 2 strategies
  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]
  #subset which output plots to show in the main paper
  in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
              "dominance_allele1","selection_coef_allele1","male_exposure_prop")
  out_cols <- c("time_to_resistance0.25","strategy")
  ggSubset <- ggSubset[, c(in_cols,out_cols) ]

@@

             #YlGnBu looks really good except that the yellow points are very faint
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold", direction='horizontal')) + 
             theme_bw() +
             theme(legend.position = "bottom") +
             #theme_minimal() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             #failing to add legend for curtis point
             #scale_fill_manual(name = "Curtis Fig.2", values = 'red', labels = 'test') +
             #scale_size_manual(name = "Curtis Fig.2", values="test") +
             #scale_shape_manual(name = "Curtis Fig.2", values="test") +             
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #!!!NOW can I add a lm fitted to the 0 points abs_diff
             geom_smooth(data=ggSubset[which(ggSubset$abs_diff==0),], method = "lm", se = FALSE, colour='lightgrey', lwd=0.5) +
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=ggSubset[which(ggSubset$abs_diff==0),], size=0.8, colour='lightgrey', shape=2, fill='white') +

             #add text for Curtis point
             geom_label(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"', hjust='"right"'), nudge_x=-0.02, size=3, colour='red')
           )       
```

@@

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2))+ #, colour=abs_diff))+

@@

             theme_bw() +
             #add point for Curtis inputs
             #geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) +
             #add a lm fitted to the 0 points abs_diff
             geom_smooth(data=df_same, method = "lm", se = FALSE) 
           )
```

>>>>

  #remove insecticide1 & 2 strategies
  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]
  #subset which output plots to show in the main paper
  in_cols <- c("start_freq_allele1", "exposure","effectiveness_ins1",
              "dominance_allele1","selection_coef_allele1","male_exposure_prop")
  out_cols <- c("time_to_resistance0.25","strategy")
  ggSubset <- ggSubset[, c(in_cols,out_cols) ]

@@

             #YlGnBu looks really good except that the yellow points are very faint
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold", direction='horizontal')) + 
             theme_bw() +
             theme(legend.position = "bottom") +
             #theme_minimal() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2), colour='red', shape=3) +
             #failing to add legend for curtis point
             #scale_fill_manual(name = "Curtis Fig.2", values = 'red', labels = 'test') +
             #scale_size_manual(name = "Curtis Fig.2", values="test") +
             #scale_shape_manual(name = "Curtis Fig.2", values="test") +             
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #!!!NOW can I add a lm fitted to the 0 points abs_diff
             geom_smooth(data=ggSubset[which(ggSubset$abs_diff==0),], method = "lm", se = FALSE, colour='lightgrey', lwd=0.5) +
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=ggSubset[which(ggSubset$abs_diff==0),], size=0.8, colour='lightgrey', shape=2, fill='white') +

             #add text for Curtis point
             geom_label(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_ins1 + effectiveness_ins2', label='"Curtis Fig.2"', hjust='"right"'), nudge_x=-0.02, size=3, colour='red')
           )       
```

@@

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2))+ #, colour=abs_diff))+

@@

             theme_bw() +
             #add point for Curtis inputs
             #geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_ins1 + effectiveness_ins2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) +
             #add a lm fitted to the 0 points abs_diff
             geom_smooth(data=df_same, method = "lm", se = FALSE) 
           )
```

### 2017-01-03 inst/documents/paper1/paper1_results_figs_slimmed_50_rr.Rmd
tidy pap1 files into own folder

plotlist[[1]] <- ggplot(df_to_plot, aes(x=generation, y=freq, 
                              colour=factor(dominance,labels=c("0   recessive",
                                                               "0.5 partial",
                                                               "1   dominant")))) + 
       theme_bw() +  
       #theme(legend.position = "bottom", legend.key = element_blank()) + 
       #guides(colour = guide_legend(reverse=TRUE)) +  
       labs(colour = "dominance") +
       ylab("Resistance Allele Frequency") +   
       #coord_trans(y = "log10") +    
       geom_line()
       #annotate('text',label='A)',x=-10, y=1.1)

@@

df_labs <- data.frame(lab=rep(c('RR','RS','SS'),4),
                      x=c(10,10,10,30,30,30,50,50,50,70,70,70),
                      y=c(50,46,42,38,34,30,26,22,18,14,10,6),
                      #col=c(2,1,1,2,1.5,1,2,2,1,2,2,2))
                      col=c(1,0,0,1,0.5,0,1,1,0,1,1,1))

df_boxes <- data.frame(lab=c('R recessive\n(slow spread)',
                             'R semi-dominant\n(rapid spread)',
                             'R dominant\n(rapid spread)',
                             'No selection for R'),
                      x=c(10,30,50,80),
                      y=c(90,75,60,35))

plotlist[[2]] <- ggplot(data.frame(x=c(0,100),y=c(80,0)), aes(x=x, y=y)) + 
       theme_bw() + 
       ylim(0,100) +
       coord_cartesian(expand = FALSE) + #so that axes fit data exactly
       ylab("Insecticide concentration") +
       xlab("Time since treatment") +         
       geom_line(size=2, colour=rgb(0.5,0,0.5)) +
       geom_vline(xintercept = c(20,40,60), linetype=2) +
       geom_text(data=df_labs,aes(x=x, y=y, label=lab, colour=factor(col)),size=4) +
       scale_colour_manual(values = c("0" = "red","0.5" = "orange","1" = "green"), guide=FALSE) +  
       geom_label(data=df_boxes,aes(x=x, y=y, label=lab)) +
       theme(axis.text = element_blank(),
             axis.ticks = element_blank(),
             panel.grid = element_blank())
       #draw_plot_label('B)') +

>>>>

plotlist[[1]] <- ggplot(df_to_plot, aes(x=generation, y=freq, 
                              colour=factor(dominance,labels=c("0   recessive",
                                                               "0.5 semi-dominant",
                                                               "1   dominant")))) + 
       theme_bw() +  
       #theme(legend.position = "bottom", legend.key = element_blank()) + 
       #guides(colour = guide_legend(reverse=TRUE)) +  
       labs(colour = "dominance") +
       ylab("Resistance Allele Frequency") +   
       #coord_trans(y = "log10") +    
       geom_line() +
       theme(axis.text.x = element_blank(),
             axis.ticks = element_blank(),
             panel.grid = element_blank())  
       #annotate('text',label='A)',x=-10, y=1.1)

@@

#22/11/16 adding extra section on left where all killed following request from Ian
#first try adding on left @-10 and modify x extent so I don't have to fiddle with all coords
df_labs <- data.frame(lab=rep(c('RR','RS','SS'),5),
                      x=c(-10,-10,-10,10,10,10,30,30,30,50,50,50,70,70,70),
                      y=seq(62,6,-4),
                      #y=c(50,46,42,38,34,30,26,22,18,14,10,6),
                      col=c(0,0,0,1,0,0,1,0.5,0,1,1,0,1,1,1))

df_boxes <- data.frame(lab=c('All killed\n(no spread)',
                             'R recessive\n(slow spread)',
                             'R semi-dominant\n(rapid spread)',
                             'R dominant\n(rapid spread)',
                             'All survive\n(no spread)'),
                      x=c(-10,10,30,50,70),
                      y=c(105,90,75,60,45))

# df_labs <- data.frame(lab=rep(c('RR','RS','SS'),4),
#                       x=c(10,10,10,30,30,30,50,50,50,70,70,70),
#                       y=c(50,46,42,38,34,30,26,22,18,14,10,6),
#                       #col=c(2,1,1,2,1.5,1,2,2,1,2,2,2))
#                       col=c(1,0,0,1,0.5,0,1,1,0,1,1,1))
# 
# df_boxes <- data.frame(lab=c('R recessive\n(slow spread)',
#                              'R semi-dominant\n(rapid spread)',
#                              'R dominant\n(rapid spread)',
#                              'No selection for R'),
#                       x=c(10,30,50,80),
#                       y=c(90,75,60,35))

plotlist[[2]] <- ggplot(data.frame(x=c(-20,85),y=c(90,15)), aes(x=x, y=y)) + 
       theme_bw() + 
       ylim(0,115) +
       xlim(-20,85) +
       coord_cartesian(expand = FALSE) + #so that axes fit data exactly
       ylab("Insecticide concentration") +
       xlab("Time since treatment") +         
       geom_line(size=2, colour=rgb(0.5,0,0.5)) +
       geom_vline(xintercept = c(0,20,40,60), linetype=2) +
       geom_text(data=df_labs,aes(x=x, y=y, label=lab, colour=factor(col)),size=4) +
       scale_colour_manual(values = c("0" = "red","0.5" = "orange","1" = "green"), guide=FALSE) +  
       geom_label(data=df_boxes,aes(x=x, y=y, label=lab),size=3) +
       theme(axis.text = element_blank(),
             axis.ticks = element_blank(),
             panel.grid = element_blank())
       #draw_plot_label('B)') +
